Benchmarking on Rigetti architecture

### 2022-10-02 txt/manuscript.tex
prproofs done and checked

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
positive semidefinite operators having trace equal to one, will be denoted
$\Omega_d$. 
 The subset of $M_d$ consisting of unitary matrices will be denoted
by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear mapping transforming $M_{d_1}$ into
$M_{d_2}$, which will be denoted 
\begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
There
exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
Jamio{\l}kowski isomorphism. 
For a given linear mapping $\Phi_M$ corresponding  Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
\begin{equation}
\mathcal{J}(\Phi) \coloneqq \sum_{i,j=1}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
and trace preserving (CPTP).
In this work we will consider a special class of quantum channels, called unitary channels. Let $U \in \UU_d$ be a unitary operator. A unitary channel
$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
\UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called a von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
seen as  a measure-and-prepare quantum channel as follows 
$
\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
$

@@

In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.  To do that, we will present an auxiliary lemma.   
\begin{lemma}\label{lemma:min-e-optimal}
Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 
\begin{equation}
\min_{E \in \diaguni_2} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond = \|\Phi_{U} - 
\Phi_\Id\|_\diamond,
\end{equation}
\end{lemma}
\todo[inline]{spr dowod}
\begin{proof} Recall that the distance between two unitary channels is given by
	$
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
	$
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$. 
	For $U = H 
	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
	\begin{equation}
	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |. 
	\end{equation} 
		It implies that it is enough to prove  \begin{equation}
		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
		\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
		\end{equation}
%		It implies that we can prove  equivalently  the following condition
%		\begin{equation}
%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
%		\end{equation}
This condition is equivalent to 
	\begin{equation}
	\max_{E \in \diaguni_2 } \nu_{E} \coloneqq \nu = \frac{|1 + e^{i \phi} | }{2},
	\end{equation}
	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $ 
	We can prove that
	\begin{equation}
	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
	\end{equation}
	So we obtain \begin{equation}
	\max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
		\Omega_2} \left| \tr \left( \rho U E \right) \right|
	\end{equation}
	For that, our task is reduce to show that
	\begin{equation}
	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \nu. 
	\end{equation}
	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
	and let us take $\rho = 
	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
	From spectral theorem, let us decompose $U$ as
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
	\end{equation}
	where  for eigenvalue $\lambda_1 = e^{i \phi}$, the corresponding 
	eigenvector is 
	of the form $\ket{x_1} = 
	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
	whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
	Then, we have 
	\begin{equation}
	\begin{split}
	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
	\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) 
	\right|  = 
	\frac{1}{2} \left| e^{i \phi}  \bra{x_1} E \ket{x_1} + \bra{x_2} E \ket{x_2} 
	\right| = \\& 
	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| 
	= 
	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
	\nu, 
	\end{split}
	\end{equation}
	which completes the proof.
\begin{theorem}
The optimal probability of correct discrimination between von Neumann
measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
where $\phi \in [0, 2\pi)$ is given by
\begin{equation}
p = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
\end{equation}
\end{theorem}
\todo[inline]{spr dowod}
\begin{proof}
	From Holevo-Helstrom theorem we obtain
	\begin{equation}
	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
	\end{equation}
	From Theorem 1 in~\cite{puchala2018strategies} we have 
	\begin{equation}
	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond. 
	\end{equation}
	From Lemma~\ref{lemma:min-e-optimal} we know that for our unitary matrix 
	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
	\begin{equation}
		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond,
	\end{equation} which is exactly equal to 
	\begin{equation}
	\|\Phi_{U} - 
	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|. 
	\end{equation}
	Finally, we obtain that
	\begin{equation}
	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
	\end{equation}
	It implies that
	\begin{equation}
	p  = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
	\end{equation} which completes the proof.

@@

%
%
%\begin{theorem}\label{rozrpomiarow}
%Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
%H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
%\not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
%form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
%	\begin{enumerate}
%		\item $\rho_1,\rho_2 \in \Omega_2$
%		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
%		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
%		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
%	\end{enumerate}
%	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
%	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of 
%	$U$. Then  we have 
%	\begin{equation}
%	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i 
%	\phi}}{2}\right|^2}.
%	\end{equation}
%	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą 
%	%wartością własną $U\in \mathrm{U}(\XX)$.
%\end{theorem}
%\begin{proof} From \ref{th:minE} we have 
%	\begin{equation}
%	\begin{split}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} 
%	||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in 
%	\diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) 
%	||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || 
%	\Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| 
%	\Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
%	\end{split}
%	\end{equation}
%The diamond norm between two unitary channels can be calculated by 
%	\begin{equation}
%	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = 
%	\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho 
%	)|^2}.
%	\end{equation}
%Hence,  it is enough to calculate the formula
%\begin{equation}
%\begin{split}
%\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
%\end{split}
%\end{equation}
%Recall, let us note $U$ as
%\begin{equation}
%U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
%\end{equation}
%where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is of 
%the form $\ket{x_1} = 
%\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
% whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
%\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
% 
%Consider two cases:
%
%	$1^\circ$ Consider $\phi = \pi$. Then $U$ is of the form
%	\begin{equation}
%	U = \left(\begin{array}{cc}0&1\\1&0\end{array}\right).
%	\end{equation}
%Then $0 \in W(U)$. 	From Proposition 3 in ~\cite{puchala2018strategies} the 
%measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if 
%and only if there exists $\rho \in \Omega_2$ such that
%	\begin{equation}
%	\mathrm{diag}\left(U^\dagger \rho\right) = 0.
%	\end{equation}
%Hence, for $U $ we have 
%	\begin{equation}
%	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} 
%	\left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right)
%	 =  \mathrm{diag} 
%	\left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
%	\end{equation}
% It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for 
% which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the 
% form
%	\begin{equation}
%	\rho = \left(\begin{array}{cc}\rho_{1,1}&0\\0&\rho_{2,2}\end{array}\right),
%	\end{equation}
%	where $\rho_{1,1},\rho_{2,2} \ge 0$ and  $\rho_{1,1}+\rho_{2,2}=1$.
%
%	$2^\circ$ Consider  $\phi \not = \pi$. 
%The spectrum of $U$ is of the form $\sigma(U) = \{e^{i \phi},1\}$. 
%Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
%	\begin{equation}
%	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
%	\end{equation}
%Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = 
%\ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 
%\in \Omega_2$ and satisfies the requirements of theorem. Hence, the 
%discriminator $\rho \in \Omega_2$ has the form 
%	\begin{equation}
%	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = 
%	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
%	\end{equation}
%%and 
%%	\begin{equation}
%%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 
%%+ e^{\mathbf{i} \phi}}{2}\right|^2 },
%%	\end{equation}
%
%	
%%	
%%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} 
%%\rho_2$ we have 
%%	\begin{equation}
%%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 
%%\right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = 
%%\frac{\lambda_1+\lambda_2}{2}. 
%%	\end{equation}
%%	Therefore, we have
%%	\begin{equation}
%%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- 
%%\left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
%%	\end{equation}
%%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 
%%e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. 
%%Then we have 
%%	\begin{equation}
%%	\begin{split}
%%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E 
%%\right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = 
%%\frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} 
%%\lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} 
%%\left(\lambda_1 
%%+ \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
%%	\end{split}
%%	\end{equation} 
%%So we have 
%%	\begin{equation}
%%	\left|\tr\left(UE \rho \right) \right| = 
%%\left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 
%%\bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} 
%%\right|.
%%	\end{equation}
%%	It implies that
%%	\begin{equation}
%%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  
%%|\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
%%	\end{equation}
%%	Hence we obtain
%%	\begin{equation}
%%	\begin{split}
%%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} 
%%\sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} 
%%\right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 
%%-\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
%%	\end{split}
%%	\end{equation
\begin{proof}
For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
\begin{equation}

>>>>

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
positive semidefinite operators having trace equal to one, will be denoted
$\Omega_d$. 
 The subset of $M_d$ consisting of unitary matrices will be denoted
by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$. 
	An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$.
Whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.

 We will also need a linear mapping transforming $M_{d_1}$ into
$M_{d_2}$, which will be denoted 
\begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
There
exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
Jamio{\l}kowski isomorphism. 
For a given linear mapping $\Phi_M$ corresponding  Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
\begin{equation}
\mathcal{J}(\Phi) \coloneqq \sum_{i,j=1}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
and trace preserving (CPTP).
In this work we will consider a special class of quantum channels, called unitary channels. Let $U \in \UU_d$ be a unitary operator. A unitary channel
$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
\UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called a von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
seen as  a measure-and-prepare quantum channel as follows 
$
\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
$

@@

In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.  To do that, we will present an auxiliary lemma.   
\begin{lemma}\label{lemma:min-e-optimal}
Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 
\begin{equation}
\min_{E \in \diaguni_2} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond = \|\Phi_{U} - 
\Phi_\Id\|_\diamond,
\end{equation}
\end{lemma}

\begin{proof} Recall that the distance between two unitary channels is given by
	$
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
	$
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$. 
	For $U = H 
	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
	\begin{equation}
	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |. 
	\end{equation} 
		It implies that it is enough to prove  \begin{equation}
		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
		\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
		\end{equation}
%		It implies that we can prove  equivalently  the following condition
%		\begin{equation}
%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
%		\end{equation}
This condition is equivalent to 
	\begin{equation}
	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
	\end{equation}
	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $

%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
 The celebrated Hausdorf-T{\o}plitz theorem~\cite{hausdorff, toeplitz} states that
$W(A)$ of any matrix $A \in M_d$ is a convex set and therefore
\begin{equation}
W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}. 
\end{equation}
So we obtain that 
	\begin{equation}
	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
	\end{equation}
	And then we have 
	 \begin{equation}
 \max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
		\Omega_2} \left| \tr \left( \rho U E \right) \right|
	\end{equation}
	For that, our task is reduce to show that
	\begin{equation}
	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \mu
	\end{equation}
	where $\mu \coloneqq \max_{E \in \diaguni_2 } \nu_{E}.$

	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
	and take $\rho = 
	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
	From spectral theorem, let us decompose $U$ as
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
	\end{equation}
	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
	eigenvector is 
	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
	$,
	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
	$.
	Then, we have 
	\begin{equation}
	\begin{split}
	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
	\frac{1}{2} \left| \tr\left((   \proj{x_1} +e^{i \phi}\proj{x_2} ) E \right) 
	\right|  = 
	\frac{1}{2} \left|  \bra{x_1} E \ket{x_1} +  e^{i \phi}\bra{x_2} E \ket{x_2} 
	\right| = \\& 
	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| 
	= 
	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
	\mu, 
	\end{split}
	\end{equation}
	which completes the proof.
\end{proof}
\begin{theorem}
The optimal probability of correct discrimination between von Neumann
measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
where $\phi \in [0, 2\pi)$ is given by
\begin{equation}
p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
\end{equation}
\end{theorem}

\begin{proof}
	From Holevo-Helstrom theorem we obtain
	\begin{equation}
p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
	\end{equation}
	From Theorem 1 in~\cite{puchala2018strategies} we have 
	\begin{equation}
	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond. 
	\end{equation}
	From Lemma~\ref{lemma:min-e-optimal} we know that for 
	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
	\begin{equation}
		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond,
	\end{equation} which is exactly equal to 
	\begin{equation}
	\|\Phi_{U} - 
	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|. 
	\end{equation}
%	Finally, we obtain that
%	\begin{equation}
%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
%	\end{equation}
	It implies that
	\begin{equation}
	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
	\end{equation} which completes the proof.
\end{proof}

@@

\begin{proof}
Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0, 
2\pi)$ be decomposed as 
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
	\end{equation}
	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
	eigenvector is 
	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
	$,
	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
	$.

For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
\begin{equation}
\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
Hence, we obtain
\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
\mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
\\ 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
\right\|_1  \\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
\\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
\end{split}
\end{equation}
One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
\ket{y}$ the following equation holds~\cite{watrous} 
\begin{equation}
\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
\beta |\braket{x}{y}|^2}.
\end{equation}
By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
\ket{i} \|}$ we have
\begin{equation}
	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
\end{equation}
Let us take  $\rho_0 =   \frac{1}{2}  	
\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
\begin{equation}
\begin{split}
||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
&= \sum_{i=0}^1  
\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
	4|\bra{i}\rho_0\ket{u_i}|^2}  \\
&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2} 
\\ 
&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1} 
	\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
&= \sum_{i=0}^1 
 \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
&= |1-e^{i \phi }|.
\end{split}
\end{equation}
Observe that
\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond  
&=  \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
\Id \otimes \sqrt{\rho} \right) \|_1 \\
&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
\end{split}
\end{equation}
Due to that, we know  
that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ is the discriminator of the problem 
of discrimination between 
$\PP_{\Id} $ and $\PP_U$ for 
$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
).      Hence we obtain that \begin{equation}
\ket{\psi_{AB}} \coloneqq   | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
\Id_2 \rangle \rangle,
\end{equation}
which completes the proof.
\end{proof}
